---
title: My dynamic report
output: html_fragment
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
```

## Tracking My Phone Entertainment Habits

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTd4RWFHtT-Nv3ncuh5V9wjgXJOOyWrOIiHYnBvaNGIxcTW2OC9OXl_iE1dVt44rH5kHtkeBw_GXnP7/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    minutes = `How many minutes did I spend on phone entertainment?`,
    activity = `What was my main activity?`,
    mood = `What was my mood at that time?`
  )

mean_minutes <- mean(latest_data$minutes)
max_minutes <- max(latest_data$minutes)

```
  
This report tracks my phone entertainment habits.

The average time spent on phone entertainment is `r round(mean_minutes, 1)` minutes.

The maximum time spent on phone entertainment is `r max_minutes` minutes.

```{r}
ggplot(latest_data, aes(x = activity)) +
  geom_bar()

ggplot(latest_data, aes(x = mood)) +
  geom_bar()
```

```{r}
library(tidyverse)

logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTd4RWFHtT-Nv3ncuh5V9wjgXJOOyWrOIiHYnBvaNGIxcTW2OC9OXl_iE1dVt44rH5kHtkeBw_GXnP7/pub?output=csv")

latest_data <- logged_data %>%
  rename(
    minutes = `How many minutes did I spend on phone entertainment?`,
    activity = `What was my main activity?`,
    mood = `What was my mood at that time?`
  )

mean_minutes <- mean(latest_data$minutes)
max_minutes <- max(latest_data$minutes)
```

This report tracks my phone entertainment habits over time.

The average time spent on phone entertainment is `r round(mean_minutes, 1)` minutes.

The maximum time spent on phone entertainment is `r max_minutes` minutes.

```{r}
ggplot(latest_data, aes(x = activity)) +
  geom_bar() +
  labs(
    title = "Main phone entertainment activity",
    x = "Activity",
    y = "Count"
  )

```

```{r}
ggplot(latest_data, aes(x = mood)) +
  geom_bar() +
  labs(
    title = "Mood during phone entertainment",
    x = "Mood",
    y = "Count"
  )